Why there are more species in several small patches vs few large patches:

### 2024-10-09 ms_SLOSS.Rmd
Updated title and Readme with zenodo

@@

The model was developed in Netlogo 6.3.0 and the model source code is available at Github <https://>, the Overview, Design concepts, Details (ODD), protocol for describing individual-based models is included within the model source code [@Grimm2010]. We performed the simulations and analysis using R version 4.3.1 [@RCoreTeam2023], the R source code to perform simulations and analysis is located at <https://>.

@@

@@

>>>>

Leonardo A. Saravia ^1^^2^, Ulises Balza ^1^, Fernando Momo^3^^4^

1. Centro Austral de Investigaciones Científicas (CADIC-CONICET). Houssay 200 (9410), Ushuaia, Argentina.

2. Universidad Nacional de Tierra del Fuego (UNTDF), Yrigoyen 879 (9410), Ushuaia, Argentina

3. Instituto de Ciencias. Universidad Nacional de General Sarmiento. J.M. Gutierrez 1159 (1613), Los Polvorines, Argentina.

4. Departamento de Ciencias Básicas. Universidad Nacional de Luján. Rutas 5 y 7, (6700) Luján. Argentina.

@@

The model was developed in Netlogo 6.3.0 and the model source code is available at Github <https://github.com/lsaravia/DynamicForestExtinction>, the Overview, Design concepts, Details (ODD), protocol for describing individual-based models is included within the model source code [@Grimm2010]. We performed the simulations and analysis using R version 4.3.1 [@RCoreTeam2023], the R source code to perform simulations and analysis is located at <https://github.com/EcoComplex/multiSLOSS>.

@@

## Author Contributions

Leonardo Saravia, Ulises Balsa, and Fernando Momo conceived the project. Leonardo Saravia designed, developed, and performed the simulations. He analyzed the data in close consultation with all co-authors. Leonardo Saravia and Ulises Balsa wrote the first draft of the manuscript. All authors contributed to the manuscript’s revision and finalization.

@@

We acknowledge the financial support provided by the "Fondo para la Investigación Científica y Tecnológica FONCYT" (Grant No. PICT-2020-SERIEA-02628). Additionally, we extend our gratitude to the National University of General Sarmiento (UNGS), especially to Dr. Santiago Doyle, for granting access to the computational resources utilized in this study.

## Conflict Of Interest Statement

We declare no conflict of interest.

## Data Availability Statement

The NetLogo model is available for download on GitHub: https://github.com/lsaravia/DynamicForestExtinction. Data and R scripts can also be accessed on GitHub: https://github.com/EcoComplex/multiSLOSS and @Saravia2024.

### 2024-10-09 ms_SLOSS_title.Rmd
Updated title and Readme with zenodo

We acknowledge the financial support provided by the "Fondo para la Investigación Científica y Tecnológica FONCYT" (Grant No. PICT-2020-SERIEA-02628). Additionally, we extend our gratitude to the National University of General Sarmiento (UNGS), especially Santiago Doyle, for granting access to the computational resources utilized in this study.

>>>>

We acknowledge the financial support provided by the "Fondo para la Investigación Científica y Tecnológica FONCYT" (Grant No. PICT-2020-SERIEA-02628). Additionally, we extend our gratitude to the National University of General Sarmiento (UNGS), especially to Dr. Santiago Doyle, for granting access to the computational resources utilized in this study.

## Conflict Of Interest Statement

We declare no conflict of interest.

## Data Availability Statement

The NetLogo model is available for download on GitHub: https://github.com/lsaravia/DynamicForestExtinction and Zenodo https://doi.org/10.5281/zenodo.8157152. Data and R scripts can also be accessed on GitHub: https://github.com/EcoComplex/multiSLOSS and Zenodo https://doi.org/10.5281/zenodo.13891484.
